Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-09 manuscript/supplements_rsfmri.Rmd
updated tables

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex")
options(knitr.kable.NA = ' ') # hide NA in tables
# set working directory of knit (RMarkdown) to directory of Rproj
```
\newpage

@@

Find in Table \@ref(tab:firstTab) to Table \@ref(tab:lastTab) with the detailed Output of the SPM Anatomy toolbox, version 2.2c. For Clusters without any labels, the toolbox was unable to assign any grey matter area.

```{r, include = FALSE}
ToolboxOutputList <- readRDS(file = "../report/tab/DetailedFCTableList.rds")
TableList_colname <- kableExtra::linebreak(c("Cluster","Number of voxels\n in cluster","\\% of cluster volume\nassigned", "Hemisphere","Area","\\% of area overlap\nwith cluster"))

TableList <- list()
for (i in 1:length(ToolboxOutputList$EntryList)){
  TableList[[i]] <-
    ToolboxOutputList$EntryList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = TableList_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = ToolboxOutputList$CaptionList[i],
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down')) #%>%
    #kableExtra::landscape()
}
```

```{r "firstTab", echo=FALSE}
i = 1
TableList[[i]] <-
    ToolboxOutputList$EntryList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = TableList_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = ToolboxOutputList$CaptionList[i],
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down')) #%>%
    #kableExtra::landscape()
TableList[[1]] 
```

```{r, echo=FALSE}
TableList[[2]]
TableList[[3]]
TableList[[4]]
TableList[[5]]
TableList[[6]]
TableList[[7]]
TableList[[8]]
```

```{r "lastTab", echo=FALSE}
i = 9
TableList[[i]] <-
    ToolboxOutputList$EntryList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = TableList_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = ToolboxOutputList$CaptionList[i],
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down')) #%>%
    #kableExtra::landscape()
TableList[[9]] 
```

>>>>

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex")
options(knitr.kable.NA = ' ') # hide NA in tables
knitr::opts_chunk$set(fig.pos = "!ht", out.extra = "")
# set working directory of knit (RMarkdown) to directory of Rproj
```
\newpage

@@

Find in the detailed Output of the SPM Anatomy toolbox, version 2.2c. For Clusters without any labels, the toolbox was unable to assign any grey matter area. Models evaluated were model 2a estimating the effects of average BMI and change in BMI, adjusting for age and sex (Table \@ref(tab:Tab2a)), then model 2b where we additionally adjusted for logmFD (Table \@ref(tab:Tab2b)), and model 2c estimating the effects of average BMI and BMI variability as well as average logmFD and change in logmFD, adjusting for age and sex (Table \@ref(tab:Tab2cfirst) to Table \@ref(tab:Tab2clast)). Last, the FD model estimating the unique effects of average logmFD and change in logmFD when adjusting for age and sex was evaluated (Table \@ref(tab:TabFDfirst) and Table \@ref(tab:TabFDlast)).

```{r, include = FALSE}
ToolboxOutputList <- readRDS(file = "../report/tab/DetailedFCTableList.rds")
TableList_colname <- kableExtra::linebreak(c("Cluster","Number of voxels\nin cluster","\\% of cluster\nvolume assigned", "Hemisphere","Area","\\% of area overlap\nwith cluster"))

TableList <- list()
for (i in 1:length(ToolboxOutputList$EntryList)){
  TableList[[i]] <-
    ToolboxOutputList$EntryList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = TableList_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = ToolboxOutputList$CaptionList[i],
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down'))
}
```

```{r Tab2a, echo=FALSE}
i = 2
ToolboxOutputList$EntryList[[i]] %>%
  knitr::kable(
    escape = FALSE,
    col.names = TableList_colname,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = ToolboxOutputList$CaptionList[i],
  ) %>%
  kableExtra::kable_styling(latex_options = c('scale_down')) 
```

```{r "Tab2b", echo=FALSE}
i = 1
ToolboxOutputList$EntryList[[i]] %>%
  knitr::kable(
    escape = FALSE,
    col.names = TableList_colname,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = ToolboxOutputList$CaptionList[i],
  ) %>%
  kableExtra::kable_styling(latex_options = c('scale_down')) 
```

```{r "Tab2cfirst", echo=FALSE}
i = 3
ToolboxOutputList$EntryList[[i]] %>%
  knitr::kable(
    escape = FALSE,
    col.names = TableList_colname,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = ToolboxOutputList$CaptionList[i],
  ) %>%
  kableExtra::kable_styling(latex_options = c('scale_down')) 
```

```{r, echo=FALSE}
TableList[[4]]
TableList[[5]]
TableList[[6]]
```

```{r "Tab2clast", echo=FALSE}
i = 7
ToolboxOutputList$EntryList[[i]] %>%
  knitr::kable(
    escape = FALSE,
    col.names = TableList_colname,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = ToolboxOutputList$CaptionList[i],
  ) %>%
  kableExtra::kable_styling(latex_options = c('scale_down')) 
```

```{r "TabFDfirst", echo=FALSE}
i = 8
ToolboxOutputList$EntryList[[i]] %>%
  knitr::kable(
    escape = FALSE,
    col.names = TableList_colname,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = ToolboxOutputList$CaptionList[i],
  ) %>%
  kableExtra::kable_styling(latex_options = c('scale_down')) 
```

```{r "TabFDlast", echo=FALSE}
i = 8
ToolboxOutputList$EntryList[[i]] %>%
  knitr::kable(
    escape = FALSE,
    col.names = TableList_colname,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = ToolboxOutputList$CaptionList[i],
  ) %>%
  kableExtra::kable_styling(latex_options = c('scale_down'))

```
